Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-27 paper.qmd
Updated Figure 4

nldr_two_curvy_original <- umap_two_curvy_scaled |> 
  ggplot(aes(x = UMAP1, y = UMAP2)) + 
  geom_point(alpha=0.5, colour="#000000", size = 0.5) +
  interior_annotation("a", sc_ltr_pos)
```

@@

proj_plot_two_curvy_true <- model_df |>
  ggplot(
    aes(
      x = proj1_from, 
      y = proj2_from)) +
  geom_point(
    color = "#000000") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.126, 0.125)) + 
  ylim(c(-0.126, 0.125)) +
  interior_annotation("a", c(0.08, 0.93), cex = 2) +
  theme(
    legend.position = "none"
  )

@@

      y = -0.2, 

@@

      yend = -0.2), #-0.35),

@@

    annotate("text", x=0.5, y=-0.25, 

@@

      x = -0.2, 

@@

      xend = -0.2, 

@@

    annotate("text", x=-0.25, y=0.25, 

@@

    annotate("text", x=-0.18, y=-0.2, 

>>>>

nldr_two_curvy_original <- umap_two_curvy_scaled |> 
  ggplot(aes(x = UMAP1, y = UMAP2)) + 
  geom_point(alpha=0.5, colour="#000000", alpha = 0.5) +
  interior_annotation("a", sc_ltr_pos)
```

@@

proj_plot_two_curvy_true <- model_df |>
  ggplot(
    aes(
      x = proj1_from, 
      y = proj2_from)) +
  geom_point(
    color = "#000000",
    alpha = 0.5) +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.126, 0.125)) + 
  ylim(c(-0.126, 0.125)) +
  interior_annotation("a", c(0.08, 0.93), cex = 2) +
  theme(
    legend.position = "none"
  )

@@

      y = -0.31, 

@@

      yend = -0.31), #-0.35),

@@

    annotate("text", x=0.5, y=-0.36, 

@@

      x = -0.25, 

@@

      xend = -0.25, 

@@

    annotate("text", x=-0.3, y=0.4, 

@@

    annotate("text", x=-0.18, y=-0.22, 
